Dominance Regions for Rank Two Cluster Algebras

### 2022-04-05 dominance_regions.tex
figures
Some more reorganization and edits

\begin{figure}[h!]
  \centering
    \newcommand{\boundingrays}{
      \tikzmath{\b = 2; \c = 2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
      \draw [color=lightgray, thick] (\xmin,0) -- (\xmax,0);
      \draw [color=lightgray, thick] (0,\ymin) -- (0,\ymax);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
      \draw [color=lightgray, thick, dashed] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
    }
  \begin{tikzpicture}[scale=.3]
    \begin{scope}[shift={(0,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l,\l) circle (6pt);
    \end{scope}
    \begin{scope}[shift={(13,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l *\b + \l, - \l) circle (6pt);
      \draw [very thick, join=round] (\l * \b + \l, -\l) -- (\l,-\l);
    \end{scope}
    \begin{scope}[shift={(26,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, \l) circle (6pt);
      \draw [very thick, join=round] (-\l, \l) -- (-\l,\l + \l*\c);
    \end{scope}
    \begin{scope}[shift={(39, 0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, -\l) circle (6pt);
      \draw [very thick, join=round] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
    \end{scope}
    \begin{scope}[shift={(0,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c -0.1; \y = -\l; }
      \fill (\x,\y) circle (6pt);
      \draw [very thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
    \end{scope}
    \begin{scope}[shift={(13,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c + 0.15; \y = -\l - 3*\l/10;}
      \fill (\x,\y) circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dash dot] (0,0);
      \draw [very thick, dash dot, join=round] (0,0) --  (\x , \y);
    \end{scope}
    \begin{scope}[shift={(26,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \l/2/\c; \y = -\l; }
      \fill (\x,\y) circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dash dot] (0,0);
      \draw [very thick, dash dot, join=round] (0,0) --  (\x , \y);
    \end{scope}
    \begin{scope}[shift={(39,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \c*\l/\b/1.03; \y = -\l; }
      \fill (\x , \y)  circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dotted] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s);
      \draw [very thick, dotted, join=round] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
      \draw [very thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
    \end{scope}
  \end{tikzpicture}
\end{figure}

@@

@@

  \section{Rank Two}
  Fix integers $b,c>0$ and assume $bc\ge 4$.
  Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
  Here we may take the 2-regular tree $\TT_2$ to have vertices labeled $t_i$ for $i\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labeled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labeled $2$.
  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC_{t_i}(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.

  Observe that $\phi_{t_1}:=\phi_1^{t_0}$ is the piecewise-linear map given by
  \begin{equation}
    \label{eq:forward mutation 1}
    \phi_{t_1}(\lambda)=\begin{cases} (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1\ge0$;}\\ (-\lambda_1,\lambda_2) & \text{if $\lambda_1<0$;} \end{cases}
  \end{equation}
  and $\phi_{t_2}:=\phi_2^{t_1}\phi_1^{t_0}$ is the piecewise-linear map given by
  \begin{equation}
    \label{eq:forward two step mutation}
    \phi_{t_2}(\lambda)=\begin{cases} \big((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2\big) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\ (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\ (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}\end{cases}
  \end{equation}
  while $\phi_{t_2}^{-1}=\phi_{t_{-2}}$ is the piecewise-linear map given by
  \begin{equation}
    \label{eq:backward two step mutation}
    \phi_{t_2}^{-1}(\lambda)=\begin{cases} \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\ (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\ (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\ (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$;}\end{cases}
  \end{equation}

  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
  \begin{lemma}
    Any nonzero eigenvector of $\phi_{t_2}$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
  \end{lemma}
  \begin{proof}
    First observe that the equation $\phi_{t_2}^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
    In this region, $\phi_{t_2}$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
    We thus require that 
    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
    or, equivalently, that
    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
    As these represent the same relation, the result immediately follows by inspection.
  \end{proof}

  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $\big(-bc\pm\sqrt{bc(bc-4)},2c\big)$.
  \begin{lemma}
    The vectors $\big(2b, -bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2b, -bc-\sqrt{bc(bc-4)}\big)$) and $\big(2c, bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2c, bc-\sqrt{bc(bc-4)}\big)$) are perpendicular.
  \end{lemma}
  \begin{proof}
    This is immediate from the equality $\big(-bc+\sqrt{bc(bc-4)}\big)\big(bc+\sqrt{bc(bc-4)}\big)=-4bc$.
  \end{proof}
  \begin{lemma}
    \label{le:imaginary stability}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{t_{2j}}(\lambda)\in\cI$ and $\phi_{t_{2j+1}}(\lambda)\in\cI'$.
  \end{lemma}
  \begin{proof}
    Note that $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ so the result follows from the cases $j=1$ and $j=0$, respectively.
    The claim is immediate for $\phi_{t_2}$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_{t_2}$ is linear in $\cI$.
    Now, since $b>0$, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_{t_1}$ in this region.
  \end{proof}

  It will be useful to have explicit expressions for $\phi_{t_i}(\lambda)$ for $\lambda\in\cI$.
  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.

  The following gives the desired expressions for $\phi_{t_i}(\lambda)$ when $\lambda\in\cI$.
  \begin{lemma}
    \label{le:imaginary transformations}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have
    \begin{align*}
      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
    \end{align*}
  \end{lemma}
  \begin{proof}
    We work by induction on $j$, the case $j=0$ being clear from the definitions.
    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$.
    For $\lambda\in\cI$, the action of $\phi_{t_2}$ from \eqref{eq:forward two step mutation} can be rewritten as
    \[\phi_{t_2}(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
    and so
    \begin{align*}
      \phi_{t_{2j+2}(\lambda)}&=\phi_{t_2}\phi_{t_{2j}}(\lambda)\\
      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
    \end{align*}
    as desired, where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.

    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the claimed formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
  \end{proof}

@@

  \section{Chebyshev}
  For this, we define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.

    given as in the figure below:
    \[
      \begin{tikzpicture}
        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
        \draw[-] (-8,0) -- (5,0);
        \draw[-] (0,-5) -- (0,5);
        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
        \draw[-] (0,0) -- (5,-2.113);
        \draw[-] (0,0) -- (3.17,-5);
        \node at (1,-0.9) {$\cI$};
        \draw[fill=black] (3.5,-3) circle (2pt);
        \node[below right] at (3.5,-3) {$\lambda$};
        \draw[->,thick] (3.5,-3) -- (47/10,-5);
        \draw[-,thick] (3.5,-3) -- (0,26/10);
        \draw[-,thick] (0,26/10) -- (-26/4,0);
        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
        \node at (4.5,-4) {\eqref{ineq:1}};
        \node at (2.5,-0.5) {\eqref{ineq:2}};
        \node at (-3,1.75) {\eqref{ineq:3}};
        \node at (-5.5,-3) {\eqref{ineq:4}};
      \end{tikzpicture}
    \]
  \end{lemma}
  \begin{proof}
    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.

>>>>

\begin{figure}[h!]
  \centering
    \newcommand{\boundingrays}{
      \tikzmath{\b = 2; \c = 2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
      \draw [color=lightgray, thick] (\xmin,0) -- (\xmax,0);
      \draw [color=lightgray, thick] (0,\ymin) -- (0,\ymax);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
      \draw [color=lightgray, thick, dashed] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
    }
  \begin{tikzpicture}[scale=.3]
    \begin{scope}[shift={(0,0)}]
      \boundingrays;
      \tikzmath{ \r=1; \s=1; \x = \r; \y=\s; }
      \fill (\x,\y) circle (6pt);
    \end{scope}
    \begin{scope}[shift={(13,0)}]
      \boundingrays;
    \tikzmath{ \r=1; \s=1; \x = \r + \b*\s; \y=-\s; }
      \fill (\x, \y) circle (6pt);
      \draw [very thick, join=round] (\x, \y) -- ({\x+\b * \y},\y);
    \end{scope}
    \begin{scope}[shift={(26,0)}]
      \boundingrays;
      \tikzmath{ \r=1; \s=1; \x=-\r; \y=\s; }
      \fill (\x, \y) circle (6pt);
      \draw [very thick, join=round] (\x, \y) -- (\x,{\y - \c * \x});
    \end{scope}
    \begin{scope}[shift={(39, 0)}]
      \boundingrays;
      \tikzmath{ \r=1; \s=1; \x=-\r; \y=-\s; }
      \fill (\x, \y) circle (6pt);
%      \draw [very thick, join=round] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
      \draw [very thick, join=round] (\x, \y) -- ({\x + \b * \y}, \y) -- ({\x + \b * \y}, {\y -\c*(\x + \b * \y)}) -- (\x, {\y - \c*\x}) -- cycle;
    \end{scope}
    \begin{scope}[shift={(0,-13)}]
      \boundingrays;
      \tikzmath{ \r=1; \s=1; \x={\r*\b+\s*(\b*\c-1) }; \y = {-\r -\c*\s};  }
      \fill (\x,\y) circle (6pt);
      \draw [very thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
    \end{scope}
    \begin{scope}[shift={(13,-13)}]
      \boundingrays;
      \tikzmath{ \r=1/2; \s=1; \x={2*\r*\b+\s*(\b*\c-1) }; \y = {-\r*\bcms -\c*\s};  }
      \fill (\x,\y) circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dash dot] (0,0);
      \draw [very thick, dash dot, join=round] (0,0) --  (\x , \y);
    \end{scope}
    \begin{scope}[shift={(26,-13)}]
      \boundingrays;
      \tikzmath{ \r=0.3; \s=1; \x={2*\r*\b }; \y = {-\r*\bcps -\s};  }
      \fill (\x,\y) circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dash dot] (0,0);
      \draw [very thick, dash dot, join=round] (0,0) --  (\x , \y);
    \end{scope}
    \begin{scope}[shift={(39,-13)}]
      \boundingrays;
      \tikzmath{ \r=0.5; \s=0.7; \x={2*(\r+\s)*\b }; \y = {-\r*\bcps -\s*\bcms};  }
      \fill (\x , \y)  circle (6pt);
      \fill ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (2pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dotted] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s);
      \draw [very thick, dotted, join=round] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
      \draw [very thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
    \end{scope}
  \end{tikzpicture}
\end{figure}

@@

The paper is organized as follows.
In Section~\ref{sec:chebyshev}, we collect useful results related to two-parameter Chebyshev polynomials which support our main calculations.

\section{Chebyshev Polynomials}
  \label{sec:chebyshev}
  Define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.

\section{Rank Two Lattice Mutations}
  We begin by studying transformations of $\RR^2$ which determine the transformation of $\bfg$-vectors under mutations.

  Write $\phi_0:\RR^2\to\RR^2$ for the identity map and define piecewise-linear maps $\phi_{\pm 1},\phi_{\pm 2}:\RR^2\to\RR^2$ as follows:
  \begin{equation}
    \phi_1(\lambda)
    =
    \begin{cases} 
      (-\lambda_1,c\lambda_1+\lambda_2) & \text{if $\lambda_1 \ge 0$;}\\
      (-\lambda_1,\lambda_2) & \text{if $\lambda_1 < 0$;}
    \end{cases}
    \qquad
    \phi_{-1}(\lambda)
    =
    \begin{cases} 
      (\lambda_1,-\lambda_2) & \text{if $\lambda_2 \ge 0$;}\\
      (\lambda_1+b\lambda_2,-\lambda_2) & \text{if $\lambda_2 < 0$;}
    \end{cases}
  \end{equation}
  \begin{equation}
    \label{eq:forward two step mutation}
    \phi_2(\lambda)
    =
    \begin{cases}
      \big((bc-1)\lambda_1+b\lambda_2, -c\lambda_1-\lambda_2\big) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$;}\\
      (-\lambda_1, -c\lambda_1-\lambda_2) & \text{if $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2<0$;}\\
      (-\lambda_1+b\lambda_2, -\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2\ge 0$;}\\
      (-\lambda_1,-\lambda_2) & \text{if $\lambda_1<0$ and $\lambda_2<0$;}
    \end{cases}
  \end{equation}
  \begin{equation}
    \label{eq:backward two step mutation}
    \phi_{-2}(\lambda)
    =
    \begin{cases}
      \big(-\lambda_1-b\lambda_2, c\lambda_1+(bc-1)\lambda_2\big) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2\le 0$;}\\
      (-\lambda_1-b\lambda_2, -\lambda_2) & \text{if $\lambda_2\le 0$ and $\lambda_1+b\lambda_2>0$;}\\
      (-\lambda_1, c\lambda_1-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1\le 0$;}\\
      (-\lambda_1,-\lambda_2) & \text{if $\lambda_2>0$ and $\lambda_1>0$.}
    \end{cases}
  \end{equation}

  For $|k|>2$, define piecewise-linear maps
  \[\phi_k
    :=
    \begin{cases}
      \phi_1\phi_2^j & \text{if $k>0$ and $k=2j+1$;}\\
      \phi_{-1}\phi_{-2}^j & \text{if $k<0$ and $k=-2j-1$;}\\
      \phi_2^j & \text{if $k>0$ and $k=2j$;}\\
      \phi_{-2}^j & \text{if $k<0$ and $k=-2j$;}\\
    \end{cases}
  \]
  and observe that $\phi_{2j}^{-1}=\phi_{-2j}$ for $j\in\ZZ$.

  \begin{definition}
    For $\lambda\in\ZZ^2$, define cones $\cC(\lambda):=\lambda-b\RR_{\ge0}+c\RR_{\ge0}$ and $\cC'(\lambda):=\lambda+b\RR_{\ge0}-c\RR_{\ge0}$.
    The \emph{dominance region} $\cP(\lambda)$ is the intersection of $\bigcap_{j\in\ZZ}\phi_{2j}^{-1}\cC(\phi_{2j}\lambda)$ and $\bigcap_{j\in\ZZ} \phi_{2j+1}^{-1}\cC'(\phi_{2j+1}\lambda)$
  \end{definition}

  By an eigenvector of a piecewise-linear map $\phi$, we will mean a vector $\lambda$ such that for each $k>0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
  \begin{lemma}
    Any nonzero eigenvector of $\phi_2$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
  \end{lemma}
  \begin{proof}
    First observe that the equation $\phi_2^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k>0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
    In this region, $\phi_2$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
    We thus require 
    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
    or equivalently
    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
    As these represent the same relationship, the result immediately follows by inspection.
  \end{proof}

  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $\big(-bc\pm\sqrt{bc(bc-4)},2c\big)$.
  %\begin{lemma}
  %  The vectors $\big(2b, -bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2b, -bc-\sqrt{bc(bc-4)}\big)$) and $\big(2c, bc+\sqrt{bc(bc-4)}\big)$ (resp. $\big(2c, bc-\sqrt{bc(bc-4)}\big)$) are perpendicular.
  %\end{lemma}
  %\begin{proof}
  %  This is immediate from the equality $\big(-bc+\sqrt{bc(bc-4)}\big)\big(bc+\sqrt{bc(bc-4)}\big)=-4bc$.
  %\end{proof}
  \begin{lemma}
    \label{le:imaginary stability}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{2j}(\lambda)\in\cI$ and $\phi_{2j+1}(\lambda)\in\cI'$.
  \end{lemma}
  \begin{proof}
    Since $\phi_{2j}=\phi_2^j$ and $\phi_{2j+1}=\phi_1\phi_{t_2}^j$, the result follows from the cases $j=1$ and $j=0$, respectively.
    The claim is immediate for $\phi_2$ since the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$ are eigenvectors and $\phi_2$ is linear in $\cI$.
    Now, since $b>0$, we have $\phi_1(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_1\Big( \big(2b,-bc\pm\sqrt{bc(bc-4)}\big) \Big)=\big(-2b,bc\pm\sqrt{bc(bc-4)}\big)$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity of $\phi_1$ in this region.
  \end{proof}

  It will be useful to have explicit expressions for $\phi_k(\lambda)$ for $\lambda\in\cI$.
  \begin{lemma}
    \label{le:imaginary transformations}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have
    \begin{align*}
      \phi_{2j}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
      \phi_{2j+1}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
    \end{align*}
  \end{lemma}
  \begin{proof}
    We work by induction on $j$, the case $j=0$ being clear from the definitions.
    For $\lambda\in\cI$, the action of $\phi_2$ from \eqref{eq:forward two step mutation} can be rewritten as
    \[\phi_2(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
    and so
    \begin{align*}
      \phi_{2j+2}(\lambda)&=\phi_2\phi_{2j}(\lambda)\\
      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
    \end{align*}
    as desired, where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.

    Similarly, using $\phi_1(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_1\phi_2^j$ gives the claimed formula for $\phi_{2j+1}$ from that of $\phi_{2j}$.
  \end{proof}

    given as in the figure below:
    \[
      \begin{tikzpicture}
        \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
        \draw[-] (-8,0) -- (5,0);
        \draw[-] (0,-5) -- (0,5);
        %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
        \draw[dashed] (0,0) -- (5,-2.113);
        \draw[dashed] (0,0) -- (3.17,-5);
        \node at (1,-0.9) {$\cI$};
        \draw[fill=black] (3.5,-3) circle (2pt);
        \node[right] at (3.5,-3) {$\lambda$};
        \draw[->,thick] (3.5,-3) -- (47/10,-5);
        \draw[-,thick] (3.5,-3) -- (0,26/10);
        \draw[-,thick] (0,26/10) -- (-26/4,0);
        \draw[->,thick] (-26/4,0) -- (-16/4,-5);
        \node at (4.5,-4) {\eqref{ineq:1}};
        \node at (2.34,-0.5) {\eqref{ineq:2}};
        \node at (-3,1.75) {\eqref{ineq:3}};
        \node at (-5.36,-3) {\eqref{ineq:4}};
      \end{tikzpicture}
    \]
  \end{lemma}
  \begin{proof}
    Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.

@@

  \section{Rank Two}

@@
